Structural controllability of ecological networks

### 2018-06-19 paper/reviewers-response.Rmd

Thanks for this observation. 
In line with feedback from both editors, we have chosen to emphasise on the conceptual aspects of the work and reduced the core question of management applications to appear only in the discussion. 
Nevertheless, we have also rewritten the introduction and took care to be clear at explaining how this study relates to and differs from previous work.

> Finally I think it is important to provide context about what kind of decisions are being made and could be informed by this approach. Who is managing plant-pollinator networks and what choices would they actually be making. Some examples should be expanded on. And also how would the outputs of this work actual inform choices and guide prioritization

XXX answer missing XXX

> "And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed. What do we need to think about in terms of key information to use this approach?"

In the previous manuscript, we discussed this uncertainty but it was buried in the Supporting Information. 
We have now added a subsection in the Methods describing how we evaluate the impact of the uncertainty induced by using visitation as a proxy of species interdependence and that induced by incomplete sampling of rare interactions (\lr{M-testing-assumptions-line}). 
We found that the structural controllability approach is robust to these two sources of uncertainty (\lr{M-testing-assumptions-results-line}). 
Further details can be found in the Supporting Information Section \@ref(S-visitation-as-proxy) and \@ref(S-undersampling). 
In addition, we also included a reference to the key information needed to apply the method in the Discussion (XXX).

### 2018-06-19 paper/manuscript.Rmd
Use uncertainty to defend the assumption tests

\R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
We tested the sensitivity of our approach to two fundamental assumptions. 
First, we tested that visitation is an appropriate proxy to infer interspecific effects. 
To do that we compared the results obtained using visitation to two alternative metrics in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance (which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants) [@neeman_framework_2009]. More details in the Supporting Information Section \@ref(S-visitation-as-proxy). 
Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the undersampling of interactions. 
To do that we compared the results obtained when using the full network and when randomly removing interactions preferentially from the weakest links in the network. 
This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).

>>>>

\R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
We tested the sensitivity of our approach to two fundamental assumptions. 
First, we tested that visitation is an appropriate proxy to infer interspecific effects. 
To do that we compared the results obtained using visitation to two alternative metrics in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009]. More details in the Supporting Information Section \@ref(S-visitation-as-proxy). 
Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the uncertainity involved with the sampling of interactions. 
To do that we compared the results obtained when using the full network and when randomly removing interactions from the weakest links in the network. 
This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).
